Identification of quality-reflecting text features using Machine Learning Techniques

### 2022-01-12 Manuscript/Manuscript_Eli.Rmd
minor commit

output: 
  html_document:
    css: "style.css"
    fig_caption: yes
bibliography: references.bib
link-citations: yes
linkcolor: blue
---
<p style= "font-size:120%"> keywords: <em> machine learning, summary writing, automatization</em></p>
<br><br><br><br><br><br>

>>>>

output: 
  html_document:
    css: "style.css"
    fig_caption: yes
bibliography: references.bib
link-citations: yes
linkcolor: blue
---
<p style= "font-size:120%"> keywords: <em> machine learning, summary writing, automatization</em></p>
<br><br><br>
